Supplemental: A System of Equations and Derivation of Sparse Constant-Pressure\slash Constant-Volume Chemical Kinetic Jacobians for \texttt{pyJac}

### 2018-09-04 derivations.tex
remove dupl

Derivatives of the falloff blending factor---except for for all but the Lindemann falloff blending factor, which is not a function of the reduced pressure---rely upon the reduced pressure derivatives developed in~\cref{s:dpr}.
First, the blending factor for each falloff reaction type will be differentiated along with any subcomponents (e.g., the $F_{cent}$ term for Troe falloff reactions).
Next, the reduced pressured derivatives given by~\cref{e:dpr_dt,e:dpr_dnj,e:dpr_de} will be substituted in and finally a generalized form for the falloff blending factor derivatives will be determined.

>>>>

Derivatives of the falloff blending factor---except for all but the Lindemann falloff blending factor, which is not a function of the reduced pressure---rely upon the reduced pressure derivatives developed in~\cref{s:dpr}.
First, the blending factor for each falloff reaction type will be differentiated along with any subcomponents (e.g., the $F_{cent}$ term for Troe falloff reactions).
Next, the reduced pressured derivatives given by~\cref{e:dpr_dt,e:dpr_dnj,e:dpr_de} will be substituted in and finally a generalized form for the falloff blending factor derivatives will be determined.
